Honey Bees - DESeq

### 2018-04-13 C_R/DESeq2/makeDataMetrics.Rmd
Count RDS files diet and virus

>>>>

    RDC <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    RDR <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    RD_DIET <- metrics[which(metrics$padj <0.05),]$ID
    saveRDS(RDC, file="RDC.Rds")
    saveRDS(RDR, file="RDR.Rds")
    saveRDS(RD_DIET, file="RD_DIET.Rds")

### 2018-04-13 N_V/DESeq2/makeDataMetrics.Rmd
Count RDS files diet and virus

    RDC <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    RDR <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    RD_DIET <- metrics[which(metrics$padj <0.05),]$ID
    saveRDS(RDC, file="RDC.Rds")
    saveRDS(RDR, file="RDR.Rds")
    saveRDS(RD_DIET, file="RD_DIET.Rds")

>>>>

    RDV <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    RDN <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    RD_VIRUS <- metrics[which(metrics$padj <0.05),]$ID
    saveRDS(RDV, file="RDV.Rds")
    saveRDS(RDN, file="RDN.Rds")
    saveRDS(RD_VIRUS, file="RD_VIRUS.Rds")
